# Datasets used in this book

```{r, echo = FALSE}
source("glossary_funcs.R")
glossary_setup()
```

```{r, echo = FALSE, results='asis'}
glossary_setup_style()
```

We'll be using a couple of different datasets throughout this book.

# STATS-19

The STATS-19 form is used by police to record the

The STATS19 dataset is available under an [Open Government Licence](https://www.nationalarchives.gov.uk/doc/open-government-licence/version/3/).

This is available from [data.gov.uk](https://www.data.gov.uk), where you can find thousands of open datasets to work with (though not all are geographic datasets).

As of February 2024, there are [over 1700 datasets available](https://www.data.gov.uk/search?filters%5Btopic%5D=Health) with the tag of 'health'.

# SAMHI

SAMHI is the Small Area Mental Health Index.

This is LSOA-level data that combines a range of things into a single index:
- NHS Mental Health-related hospital Attendances
- Antidepressant prescribing
- Depression (as measured by the QOF)
- Department for Work and Pensions (DWP) data on Incapaacity benefit and employment support allowance for mental health

The STATS19 dataset is available under an [Open Government Licence](https://www.nationalarchives.gov.uk/doc/open-government-licence/version/3/).

Daras K, Barr B (2021), Small Area Mental Health Index (SAMHI) <VERSION 4.00> [Open Dataset], Place-based Logitudinal Data Resource, DOI: 10.17638/datacat.liverpool.ac.uk/1188

# TIA clinics

A TIA is a transient ischaemic attack. This is sometimes referred to as a 'mini-stroke', and it can be a precursor to a larger stroke. [TODO: SOURCE]


# Where to find more datasets

[Office for National Statistics - Open Geography Portal](https://geoportal.statistics.gov.uk/)

[data.gov.uk](https://www.data.gov.uk)
