# Welcome!

```{r, echo = FALSE}
source("glossary_funcs.R")
glossary_setup()
```

```{r, echo = FALSE, results='asis'}
glossary_setup_style()
```

Welcome to this HSMA book on *Geographic Modelling & Visualisation*.
<div class="tenor-gif-embed" data-postid="13892258" data-share-method="host" data-aspect-ratio="1.5625" data-width="30%"><a href="https://tenor.com/view/lost-kermit-map-where-am-i-gif-13892258">Lost Kermit GIF</a>from <a href="https://tenor.com/search/lost-gifs">Lost GIFs</a></div> <script type="text/javascript" async src="https://tenor.com/embed.js"></script>

This book accompanies module 3 of the 15 month [HSMA programme](https://sites.google.com/nihr.ac.uk/hsma/home).

It is aimed at people with some experience of Python who want to be able to work with geographic data.

It is particularly aimed at people in the UK working in the National Health Service (NHS), policing, social care, public health or local government.

We will cover topics including:

- principles and terminology needed when working with geographical data and maps
- creating maps using a free and open source software package (QGIS)
- working with geographic data in Python using the Geopandas library
- creating static maps in Python with matplotlib
- creating interactive maps in Python with Folium, Leaflet and Kepler
- interacting with travel time `r glossary("API", "APIs")`
- visualising travel times to sites across regions
- optimizing the locations of facilities to minimize travel time across a region
- optimizing the locations of facilities to maximize performance against multiple objectives (e.g. minimizing average travel time while maximizing the percentage of people who can reach a service within 30 minuts)



```{r, echo = FALSE}
glossary_table(TRUE)
glossary_reset()
```
