# Mapping in QGIS

```{r, echo = FALSE}
source("glossary_funcs.R")
glossary_setup()
```

```{r, echo = FALSE, results='asis'}
glossary_setup_style()
```

Small-scale problems in health can be supported with a combination of simple mapping and analysis!

You probably already have some very useful data in your organisation.

- Where are service users located?
    - What is the relative rate of users in different areas?
    - How does this interact with demographic factors (e.g. age, deprivation)?
    - Are there areas where you're getting less people attending than others that may indicate an access problem?

- Where are your services located?
    - How does this interact with demographic factors (e.g. deprivation)?
    - Are they near to bus stops, train stations, car parks etc?

There are a number of different tools you could use to make maps.

The one you'll often hear about is [ArcGIS](https://www.arcgis.com/index.html), made by ESRI.

However, ArcGIS has a licencing cost, which can put it out of reach of organisations.

One powerful `r glossary ("FOSS")` option is [QGIS](https://qgis.org/en/site/). It's used widely across both industry and the charity sector, and it's what we'll be using for this section.

If you are on the HSMA programme, it has been taught for several years, so it may have already been approved for installing in your organisation - check your organisation's software centre if you have one, or if it's on a list of approved software on your company IT portal.

Now, GIS is just "software that blends the power of a map with the power of a database to allow people to create, manage and analyse information, particularly information about location."^[Ordnance Survey](https://www.ordnancesurvey.co.uk/business-government/tools-support/gis/what-is-gis)

In later modules, we will explore how to do mapping from within Python, which will allow you to create 'static' maps (non-interactive images where you can control exactly how the final output looks), and 'interactive' maps (where a user can move around the map, zoom in or out, and interact with elements on the map to get more information). However, learning to create maps in Python doesn't make your QGIS knowledge redundant - it's a very powerful tool that is also accessible to those who don't know how to code.

# References
