# Exercises - QGIS
```{r, echo = FALSE}
source("glossary_funcs.R")
glossary_setup()
```

```{r, echo = FALSE, results='asis'}
glossary_setup_style()
```


# QGIS Exercise 1

Create a new QGIS file

Load in a basemap

Load in the STATS19 dataset (stats19_collisions_point_data_2022.csv)

Filter to one particular police force

Create one (or more) layers using point data, choosing the field(s) you find interesting

Remember that you can hide certain categories of data, change icons, add labels, filter…

# QGIS Exercise 2

Create a new QGIS file

Load in a basemap

Let’s try creating some more maps for the STATS19 dataset.

We’re just going to use a geojson file that already has some counts per MSOA joined in.
`stats_19_counts_by_msoa_3857.geojson`

Create at least one choropleth (from this file)

Try out different filters, colour schemes and categorisation modes.

# QGIS Exercise 3

Create a new QGIS file

Load in a basemap

To account for the range in size of MSOA, we now have a new csv of data with standardised values (number of collisions per square kilometre, number of casualties per 1000 occupants).

Import this csv as delimited data.

Import the vector file of MSOAs

Join these layers together

Create a print layout that shows two maps side-by-side for your region.
