# Types of Geographic Problems
```{r, echo = FALSE}
source("glossary_funcs.R")
glossary_setup()
```

```{r, echo = FALSE, results='asis'}
glossary_setup_style()
```

For the purpose of this book, we're considering geospatial problems to be ay delivery or service configuration problem that is related to and/or complicated by geography.

These can include

- Routing and Scheduling Problems
- Location-allocation Problems

| Where? (the 'geographic')              | Predictions (the 'modelling')  |
|----------------------------------------|--------------------------------|
| Where to place services…               | … if demand continues to grow? |
| Where will patients go…                | … if we close these services?  |
| Where are people with a given disease… | … and how is it spreading?     |
| Where is the demand…                   | … and is access equitable?     |


## Simple Mapping Problems - Understanding the Geographical Distribution of a Variable

Talk about disease distributions, IMD, etc.

```{python}

```

## Location Optimization (Facility Location) Problems

Talk about simple location optimization, competing priorities, etc.

## Routing and Scheduling Problems

If you've ordered an item for delivery in the past few years, you may have found yourself looking at a link sent to you by a delivery company, showing you where your delivery driver is and how many stops there are until they arrive with you.

Delivery drivers can have hundreds of parcels to deliver in a day, and companies have tens of thousands of packages to coordinate delivering. They want to keep fuel costs down and use as few vehicles as possible - so optimizing the route of each vehicle is crucial.

Now, while health systems certainly have inventory and delivery problems, there are other kinds of resources that are often travelling - nurses.

Community nursing is a huge part of the NHS. In acute (physical) trusts, nurses may be visiting the homes of clients to change dressings, conduct health checks, administer medication, and more.


```{mermaid}
flowchart LR
    id1{{"Beryl can’t do leg dressing changes for patients at the moment because she has a bad back"}}

    id2{{"Mr H only wants male nurses for the catheter change"}}

    id3{{"We need two nurses for that visit"}}

    id4{{"There are roadworks on Quarry lane for the next three weeks so it’s taking 20 minutes extra to get between visits"}}

    id5{{"Matt hasn’t done his insulin pump training yet"}}
```


Community transport problems are another class of routing problem in the NHS.
Patients are sometimes unable to get themselves to crucial appointments by driving or public transport, meaning transport vehicles are necessary to ensure they can attend critical appointements such as dialysis.

[PUT IN COVID DIALYSIS TRANSPORT EXAMPLE]

In other situations, such as mental health trusts, there may be a requirement to securely transport patients from their home to a ward for inpatient treatment, or between wards with different levels of security or treatment intensity.

This is before we start to consider things such as paramedic cars and ambulances, where the location and movement of vehicles is crucial.
